Model matters with restricted Boltzmann machines

### 2016-12-16 presentations/amherst/slides.Rmd
some more cutting

- A restricted Boltzman machine (RBM) is an undirected probabilistic graphical model with
    1. Discrete or continuous random variables 
    2. two layers - one hidden and one visible
    3. conditional independence within a layer [@smolensky1986information]

@@

RBM models exhibit *near-degeneracy* when random variables in the neg-potential function 
$$Q_{\boldsymbol \theta}(\boldsymbol x) = \sum\limits_{i = 1}^{\nv} \sum\limits_{j=1}^{\nh} \theta_{ij} v_i h_j + \sum\limits_{i = 1}^\nv\theta_{v_i} v_i + \sum\limits_{j = 1}^\nh\theta_{h_j} h_j,
$$ 
have a mean vector $\boldsymbol \mu(\boldsymbol \theta)$ close to the boundary of the convex hull of $\mathcal{T} = \{\boldsymbol t(x): x \in \mathcal{C}^{\nh + \nv}\}$ [@handcock2003assessing], where $\boldsymbol t(\boldsymbol x) = \{v_1, \dots, v_{\nv}, h_1, \dots, h_{\nh}, v_1 h_1, \dots, v_{\nv} h_{\nh} \}$ and the mean parameterization on the model parameters, $\boldsymbol \mu(\boldsymbol \theta) = \text{E}_{\boldsymbol \theta} \boldsymbol t(\boldsymbol X)$.

@@

@schweinberger2011instability introduced a concept of model deficiency related to *instability* considering only a class of exponential families of distributions.

To quantify *instability* in the RBM, it is useful to consider how a data model might be expanded to incorporate more visibles. For this, it becomes necessary to grow the number of model parameters in a sequence $\boldsymbol \theta_{\nv} \in \mathbb{R}^{\nv + \nh + \nv*\nh}, \nv \ge 1$ (one may also arbitrarily expand the number of hidden variables used).

@@

S-unstable RBM model sequences are undesirable for several reasons. Again, one is that small changes in data can lead to overly-sensitive changes in probability.

@@

Consider, for example, the biggest log-probability ratio for a one-pixel (one component) change in data outcomes (visibles).

@@

\begin{result}
\label{prop:instab}
Let $C > 0$ and $\nv \ge 1$. If $\frac{1}{\nv}\text{ELPR}(\boldsymbol \theta_\nv) > C$, then $\Delta(\boldsymbol \theta_\nv) > C$.
\end{result}

@@

Unstable RBM model sequences are connected to degenerate model sequences (placing all probability on a small portion of their sample spaces). Define a modal set

\small
\begin{align*}
M_{\epsilon, \boldsymbol \theta_\nv} &\equiv \left\{\boldsymbol v \in \mathcal{C}^\nv: \log P_{\boldsymbol \theta_\nv}(\boldsymbol v)  > (1-\epsilon)\max\limits_{\boldsymbol v^*}P_{\boldsymbol \theta_\nv}(\boldsymbol v^*) + \epsilon\min\limits_{\boldsymbol v^*}P_{\boldsymbol \theta_\nv}(\boldsymbol v^*) \right\}
\end{align*}

\normalsize
of possible outcomes, for a given $0 < \epsilon < 1$.

@@

As a consequence of unstable models, all probability will stack up on mode sets or potentially those few outcomes with the highest probability. Proofs of results \ref{prop:instab}-\ref{prop:degen} are provided later.

@@

A measure of this is the magnitude of the difference between model expectations, E$\left[\boldsymbol X | \boldsymbol \theta\right]$, and expectations given independence, E$\left[\boldsymbol X | \boldsymbol \theta^* \right]$, where $\boldsymbol \theta^*$ is defined to equal $\boldsymbol \theta$ with all $\theta_{ij} = 0$ for $i = 1, \dots, \nv, j = 1, \dots, \nh$.

Using this, it is possible to investigate what parameters lead to uninterpretability in a model versus those that guarantee interpretability.

If $|\text{E}\left[\boldsymbol X | \boldsymbol \theta\right] - \text{E}\left[\boldsymbol X | \boldsymbol \theta^*\right]|$ is large then the RBM with parameter vector $\boldsymbol \theta$ is *uninterpetable*.

@@

\begin{figure}
\includegraphics[width=.55\linewidth]{images/toyhull_top.png}
\includegraphics[width=.35\linewidth]{images/toyhull_top_2.png}
\caption{The convex hull of the "statistic space" $\mathcal{T} = \{(v_1, h_1, v_1 h_1): v_1, h_1 \in \mathcal{C}\}$ in three dimensions for the toy RBM with one visible and one hidden node for $\mathcal{C} = \{0,1\}$ (left) and $\mathcal{C} = \{-1,1\}$ (right) data encoding. The convex hull of $\mathcal{T} \subset \mathcal{C}^3$ does not fill the unit cube $[0,1]^3$ (left), but does better with $[-1,1]^3$ (right).}
\end{figure}

@@

- To explore the behavior of the RBM parameters $\boldsymbol \theta$ as it relates to near-degeneracy, instability, and uninterpretability, we consider models of small size.  For $\nh, \nv \in \{1, \dots, 4\}$, we sample `r dim(res$samp[[1]])[1]` values of $\boldsymbol \theta$.
    1. Split $\boldsymbol \theta$ into $\boldsymbol \theta_{interaction}$ and $\boldsymbol \theta_{main}$, in reference to which sufficient statistics the parameters correspond to.
    2. Allow the two types of terms to have varying average magnitudes, $||\boldsymbol \theta_{main} || /(\nh+\nv)$ and $||\boldsymbol \theta_{interaction} || /(\nh*\nv)$.
    3. Average magnitudes vary on a grid between `r min(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V))` and `r max(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V))` with `r length(unique(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V)))` breaks, yielding `r length(unique(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V)))^2` grid points.
- Calculate the three metrics of model impropriety, $\boldsymbol \mu(\boldsymbol \theta)$, $\text{ELPR}(\boldsymbol x)/\nv$, and the coordinates of $\left|\text{E}\left[\boldsymbol X | \boldsymbol \theta\right] -   \text{E}\left[\boldsymbol X | \boldsymbol \theta^* \right] \right|$. 
- In the case of *near-degeneracy*, we can go further and classify each model as near-degenerate or "viable" based on the distance of $\boldsymbol \mu(\boldsymbol \theta)$ from the boundary of the convex hull of $\mathcal{T}$

@@

```{r, fig.show="hold", fig.width=3, out.width='.32\\linewidth', fig.cap="\\label{fig:degen_plots}Results from the numerical experiment, here looking at the fraction of models that were near-degenerate (left), the sample mean value of $\\text{ELPR}(\\boldsymbol \\theta)/\\nv$ (middle), and the sample mean of the maximum component of the absolute difference between the model expectation vector, E$\\left[\\boldsymbol X | \\boldsymbol \\theta\\right]$, and the expectation vector given independence, E$\\left[\\boldsymbol X | \\boldsymbol \\theta^* \\right ]$ (right)."}
p.degen
p.elpr
p.exp_diff
```

@@

- Typically, fitting a RBM via maximum likelihood (ML) methods will be infeasible mainly due to the intractibility of the normalizing term $\gamma(\boldsymbol \theta)$ in a model of any realistic size
    - Ad hoc methods are used instead, which aim to avoid this problem by using stochastic ML that employ a small number of MCMC draws. 
- Computational concerns are not the only issues with fitting a RBM using ML, the RBM model, has the potential to re-create any distribution for the data.
    - Based on a random sample of visible variables, the model for the cell probabilities that has the highest likelihood over  *all possible model classes* is the empirical distribution, and the parametrization of the RBM model itself ensures that this empirical distribution can be arbitrarily well approximated.
    - Whenever the empirical distribution contains empty cells, fitting steps for the RBM model will aim to chase parameters that necessarily diverge in magnitude in order to zero out the corresponding RBM cell probabilities.

@@

- We consider what might be done in a principled manner, testing on a $\nv = \nh = 4$ case that already stretched the limits of what is computable - in particular we consider Bayes methods. 
- To avoid model impropriety for a fitted RBM, we want to avoid parts of the parameter space $\mathbb{R}^{\nv + \nh + \nv*\nh}$ that lead to *near-degeneracy*, *instability*, and *uninterpretability*.
    - Shrink $\boldsymbol \theta$ toward $\boldsymbol 0$ by specifying priors that place low probability on large values of $||\boldsymbol \theta||$, shrinking $\boldsymbol \theta_{interaction}$ more than $\boldsymbol \theta_{main}$.
  - We considered a test case with $\nv = \nh = 4$ and parameters given in in appendix. This parameter vector was chosen as a sampled value of $\boldsymbol \theta$ that was not near the convex hull of the sufficient statistics for a grid point in figure \ref{fig:degen_plots} with $< 5$\% near-degeneracy. We simulated $n = 5,000$ as a training set and fit the RBM using three Bayes methodologies.

@@

1. *A "trick" prior (BwTPLV).* Cancel out normalizing term in the likelihood, resulting full conditionals of $\boldsymbol \theta$ are multivariate Normal, $h_j$ are carried along as latent variables.
    \begin{align*}
    \pi(\boldsymbol \theta) \propto \gamma(\boldsymbol \theta)^n \exp\left(-\frac{1}{2C_{1}}\boldsymbol \theta_{main}'\boldsymbol \theta_{main} -\frac{1}{2C_{2}}\boldsymbol \theta_{interaction}'\boldsymbol \theta_{interaction}\right), \vspace{-.75cm}
    \end{align*}
    where $C_{2} < C_{1}$.
    This is the method of @li2014biclustering. 
2. *A truncated Normal prior (BwTNLV).* Independent spherical normal distributions as priors for $\boldsymbol \theta_{main}$ and $\boldsymbol \theta_{interaction}$, with $\sigma_{interaction} < \sigma_{main}$, *truncated* at $3\sigma_{main}$ and $3\sigma_{interaction}$, respectively. Simulation from the posterior using a geometric adaptive MH step [@zhou2014some], $h_j$ are carried along in the MCMC implementation as latent variables. 
3. *A truncated Normal prior and marginalized likelihood (BwTNML).* Marginalize out $\boldsymbol h$ in $f_{\boldsymbol \theta}(\boldsymbol x)$, and use the truncated Normal priors applied to the marginal probabilities for visible variables.

@@

# Appendix: Proof of Result \ref{prop:instab}
\scriptsize

We prove the contrapositive. Suppose that $\Delta(\boldsymbol \theta_\nv) \le C$ holds for some $C > 0$. Under the RBM model for visibles, $P_{\boldsymbol \theta_\nv}(\boldsymbol v) > 0$ holds for each outcome $\boldsymbol v \in \mathcal{C}^\nv$. Let $\boldsymbol v_{min} \equiv \argmin\limits_{\boldsymbol v \in \mathcal{C}^\nv}P_{\boldsymbol \theta_\nv}(\boldsymbol v)$ and $\boldsymbol v_{max} \equiv \argmax\limits_{\boldsymbol v \in \mathcal{C}^V\nv}P_{\boldsymbol \theta_\nv}(\boldsymbol v)$. Note there exists a sequence $\boldsymbol v_{min} \equiv \boldsymbol v_0, \boldsymbol v_1, \dots, \boldsymbol v_k \equiv \boldsymbol v_{max}$ in $\mathcal{C}^\nv$ of component-wise switches to move from $\boldsymbol v_{min}$ to $\boldsymbol v_{max}$ in the sample space (i.e. $\boldsymbol v_i, \boldsymbol v_{i + 1} \in \mathcal{C}^\nv$ differ by exactly $1$ component for $i = 0, \dots, k$) for some integer $k \in \{0, 1, \dots, \nv\}$. Then
\begin{align*}
\log\left[\frac{P_{\boldsymbol \theta_\nv}(\boldsymbol v_{max})}{P_{\boldsymbol \theta_\nv}(\boldsymbol v_{min})}\right] &= \left|\sum\limits_{i = 1}^k\log\left(\frac{P_{\boldsymbol \theta_\nv}(\boldsymbol v_i)}{P_{\boldsymbol \theta_\nv}(\boldsymbol v_{i-1})}\right)\right| \\
& \le \sum\limits_{i = 1}^k\left|\log\left(\frac{P_{\boldsymbol \theta_\nv}(\boldsymbol v_i)}{P_{\boldsymbol \theta_\nv}(\boldsymbol v_{i-1})}\right)\right| \\
& \le k \Delta(\boldsymbol \theta_\nv) \le \nv C
\end{align*}
using $k \le \nv$ and $\Delta(\boldsymbol \theta_\nv) \le C$.$\Box$

# Appendix: Proof of Result \ref{prop:degen}

Define $\boldsymbol v_{max}$ and $\boldsymbol v_{min}$ as in the proof of Proposition \ref{prop:instab}. Fix $0 < \epsilon < 1$ Then, $\boldsymbol v_{max} \in M_{\epsilon, \boldsymbol \theta_\nv}$, so $P_{\boldsymbol \theta_\nv}(M_{\epsilon, \boldsymbol \theta}) \ge P_{\boldsymbol \theta_\nv}(\boldsymbol v_{max})$. If $\boldsymbol v \in \mathcal{C}^\nv \setminus M_{\epsilon, \boldsymbol \theta_\nv}$, then by definition $P_{\boldsymbol \theta_\nv}(\boldsymbol v) \le [P_{\boldsymbol \theta_\nv}(\boldsymbol v_{max})]^{1-\epsilon}[P_{\boldsymbol \theta_\nv}(\boldsymbol v_{min})]^{\epsilon}$ holds so that
\begin{align*}
1-P_{\boldsymbol \theta_\nv}(M_{\epsilon, \boldsymbol \theta_\nv}) &= P_{\boldsymbol \theta_\nv}(M_{\epsilon, \boldsymbol \theta_\nv}^C) \\
& = \sum\limits_{\boldsymbol v \in \mathcal{C}^\nv \setminus M_{\epsilon, \boldsymbol \theta_\nv}}P_{\boldsymbol \theta_\nv}(\boldsymbol v) \\
& \le (2^\nv)[P_{\boldsymbol \theta_\nv}(\boldsymbol v_{max})]^{1-\epsilon}[P_{\boldsymbol \theta_\nv}(\boldsymbol v_{min})]^{\epsilon}
\end{align*}
Then,
\begin{align*}
\frac{1}{\nv}\log\left[\frac{P_{\boldsymbol \theta_\nv}(M_{\epsilon, \boldsymbol \theta_\nv})}{1-P_{\boldsymbol \theta_\nv}(M_{\epsilon, \boldsymbol \theta_\nv})}\right] & \ge \frac{1}{\nv} \log\left[\frac{P_{\boldsymbol\theta_\nv}(\boldsymbol v_{max})}{(2^\nv)[P_{\boldsymbol \theta_\nv}(\boldsymbol v_{max})]^{1-\epsilon}[P_{\boldsymbol \theta_\nv}(\boldsymbol v_{min})]^{\epsilon}}\right] \\
&= \frac{\epsilon}{\nv} \log\left[\frac{P_{\boldsymbol \theta_\nv}(\boldsymbol v_{max})}{P_{\boldsymbol \theta_\nv}(\boldsymbol v_{min})}\right] - \log 2 \rightarrow \infty
\end{align*}
as $\nv \rightarrow \infty$ by the definition of an unstable RBM model.$\Box$

>>>>

A restricted Boltzman machine (RBM) is an undirected probabilistic graphical model with

1. Discrete or continuous random variables 
2. two layers - one hidden and one visible
3. conditional independence within a layer [@smolensky1986information]

@@

RBM models exhibit *near-degeneracy* when random variables in 
$$Q_{\boldsymbol \theta}(\boldsymbol x) = \sum\limits_{i = 1}^{\nv} \sum\limits_{j=1}^{\nh} \theta_{ij} v_i h_j + \sum\limits_{i = 1}^\nv\theta_{v_i} v_i + \sum\limits_{j = 1}^\nh\theta_{h_j} h_j,
$$ 
have a mean vector $\boldsymbol \mu(\boldsymbol \theta)$ close to the boundary of the convex hull of $\mathcal{T} = \{\boldsymbol t(x): x \in \mathcal{C}^{\nh + \nv}\}$ [@handcock2003assessing], where $$\boldsymbol t(\boldsymbol x) = \{v_1, \dots, v_{\nv}, h_1, \dots, h_{\nh}, v_1 h_1, \dots, v_{\nv} h_{\nh} \}$$ and $$\boldsymbol \mu(\boldsymbol \theta) = \text{E}_{\boldsymbol \theta} \boldsymbol t(\boldsymbol X)$$.

@@

- Concept of model deficiency related to *instability* for a class of exponential families of distributions [@schweinberger2011instability]
- For the RBM, consider how a data model might be expanded to incorporate more visibles
    - Necessary to grow the number of model parameters in a sequence $\boldsymbol \theta_{\nv} \in \mathbb{R}^{\nv + \nh + \nv*\nh}, \nv \ge 1$ 
    - May also arbitrarily expand the number of hidden variables used.

@@

S-unstable RBM model sequences are undesirable for several reasons - small changes in data can lead to overly-sensitive changes in probability.

@@

Consider the biggest log-probability ratio for a one-pixel (one component) change in data outcomes (visibles)

@@

\begin{result}
\label{prop:instab}
Let $c > 0$ and let $\text{ELPR}(\boldsymbol \theta_\nv)$ be as in (\ref{eqn:elpr}) for an integer $\nv \ge 1$. If $\frac{1}{\nv}\text{ELPR}(\boldsymbol \theta_\nv) > c$, then $\Delta(\boldsymbol \theta_\nv) > c$.
\end{result}

@@

Define an arbitrary modal set of possible outcomes (i.e. set of highest probability outcomes) for a given $0 < \epsilon < 1$ as

\small
\begin{align*}
M_{\epsilon, \boldsymbol \theta_\nv} \equiv \left\{\boldsymbol v \in \mathcal{C}^\nv: \log P_{\boldsymbol \theta_\nv}(\boldsymbol v) > (1-\epsilon)\max\limits_{\boldsymbol v^*}P_{\boldsymbol \theta_\nv}(\boldsymbol v^*) + \epsilon\min\limits_{\boldsymbol v^*}P_{\boldsymbol \theta_\nv}(\boldsymbol v^*) \right\}
\end{align*}
\normalsize

@@

- All probability will stack up on mode sets or potentially those few outcomes with the highest probability 
- Proofs of results \ref{prop:instab}-\ref{prop:degen} can be found in [@kaplan2016note]

@@

- Measure: the magnitude of the difference between
    1. Model expectations, E$\left[\boldsymbol X | \boldsymbol \theta\right]$, and 
    2. Expectations given independence, E$\left[\boldsymbol X | \boldsymbol \theta^* \right]$, where $\boldsymbol \theta^*$ matches $\boldsymbol \theta$ for all main effects but otherwise has $\theta_{ij} = 0$ for $i = 1, \dots, \nv, j = 1, \dots, \nh$
- If $|\text{E}\left[\boldsymbol X | \boldsymbol \theta\right] - \text{E}\left[\boldsymbol X | \boldsymbol \theta^*\right]|$ is large then the RBM with parameter vector $\boldsymbol \theta$ is *uninterpetable*

@@

\begin{figure}
\includegraphics[width=.55\linewidth]{images/toyhull_top.png}
\includegraphics[width=.35\linewidth]{images/toyhull_top_2.png}
\caption{The convex hull of the "statistic space" $\mathcal{T} = \{(v_1, h_1, v_1 h_1): v_1, h_1 \in \mathcal{C}\}$ in three dimensions for the toy RBM with one visible and one hidden node for $\mathcal{C} = \{0,1\}$ (left) and $\mathcal{C} = \{-1,1\}$ (right) data encoding.}
\end{figure}

The convex hull of $\mathcal{T} \subset \mathcal{C}^3$ does not fill the unit cube $[0,1]^3$ (left), but does better with $[-1,1]^3$ (right).

@@

- To explore the behavior of the RBM parameters $\boldsymbol \theta$ as it relates to *near-degeneracy*, *instability*, and *uninterpretability*, consider models of small size  
- For $\nh, \nv \in \{1, \dots, 4\}$, sample `r dim(res$samp[[1]])[1]` values of $\boldsymbol \theta$
    1. Split $\boldsymbol \theta$ into $\boldsymbol \theta_{interaction}$ and $\boldsymbol \theta_{main}$, in reference to which sufficient statistics the parameters correspond to
    2. Allow the two types of terms to have varying average magnitudes, $||\boldsymbol \theta_{main} || /(\nh+\nv)$ and $||\boldsymbol \theta_{interaction} || /(\nh*\nv)$
    3. Average magnitudes vary on a grid between `r min(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V))` and `r max(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V))` with `r length(unique(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V)))` breaks, yielding `r length(unique(plot_dat_grid$r1/(plot_dat_grid$H + plot_dat_grid$V)))^2` grid points
- Calculate metrics of model impropriety, $\boldsymbol \mu(\boldsymbol \theta)$, $\text{ELPR}(\boldsymbol \theta)/\nv$, and the coordinates of $\left|\text{E}\left[\boldsymbol X | \boldsymbol \theta\right] - \text{E}\left[\boldsymbol X | \boldsymbol \theta^* \right] \right|$. 
- In the case of *near-degeneracy*, classify each model as near-degenerate or "viable" based on the distance of $\boldsymbol \mu(\boldsymbol \theta)$ from the boundary of the convex hull of $\mathcal{T}$

@@

```{r, fig.show="hold", fig.width=3, out.width='.32\\linewidth', fig.cap="\\label{fig:degen_plots}The fraction of models that were near-degenerate (left), the sample mean value of $\\text{ELPR}(\\boldsymbol \\theta)/\\nv$ (middle), and the sample mean of the maximum component of the absolute difference between the model expectation vector, E$\\left[\\boldsymbol X | \\boldsymbol \\theta\\right]$, and the expectation vector given independence, E$\\left[\\boldsymbol X | \\boldsymbol \\theta^* \\right ]$ (right)."}
p.degen
p.elpr
p.exp_diff
```

@@

1. Computational concerns
    - Fitting a RBM via maximum likelihood (ML) methods infeasible due to the intractibility of the normalizing term $\gamma(\boldsymbol \theta)$
        - Ad hoc methods are used, aim to avoid this problem by using stochastic ML 
        - employ a small number of MCMC draws to approximate $\gamma(\boldsymbol \theta)$ 
2. With $\nh$ large enough 
    - Potential to re-create any distribution for the data [@le2008representational; @montufar2011refinements; and @montufar2011expressive]
        - The model for the cell probabilities that has the highest likelihood over  *all possible model classes* is the empirical distribution
        - The RBM model ensures that this empirical distribution can be arbitrarily well approximated
    - When empirical distribution contains empty cells, fitting will chase parameters to $\infty$ in order to zero out the corresponding RBM cell probabilities

@@

- Consider what might be done in a principled manner, testing on $\nv = \nh = 4$ 
- To avoid model impropriety, we want to avoid parts of the parameter space $\mathbb{R}^{\nv + \nh + \nv*\nh}$ that lead to *near-degeneracy*, *instability*, and *uninterpretability*.
    - Shrink $\boldsymbol \theta$ toward $\boldsymbol 0$ 
        1. Specify priors that place low probability on large values of $||\boldsymbol \theta||$
        2. Shrink $\boldsymbol \theta_{interaction}$ more than $\boldsymbol \theta_{main}$
- Consider a test case with $\nv = \nh = 4$ and parameters given in in appendix 
    - $\boldsymbol \theta$ chosen as a sampled value from a grid point in figure \ref{fig:degen_plots} with $< 5$\% near-degeneracy (not near the convex hull of the sufficient statistics) 
    - simulate $n = 5,000$ as a training set and fit the RBM using three Bayes methodologies

@@

1. *A "trick" prior (BwTPLV).* Cancel out normalizing term in the likelihood, resulting full conditionals of $\boldsymbol \theta$ are multivariate Normal, $h_j$ are carried along as latent variables
    \begin{align*}
    \pi(\boldsymbol \theta) \propto \gamma(\boldsymbol \theta)^n \exp\left(-\frac{1}{2C_{1}}\boldsymbol \theta_{main}'\boldsymbol \theta_{main} -\frac{1}{2C_{2}}\boldsymbol \theta_{interaction}'\boldsymbol \theta_{interaction}\right), \vspace{-.75cm}
    \end{align*}
    where $C_{2} < C_{1}$ [@li2014biclustering] 
2. *A truncated Normal prior (BwTNLV).* Independent spherical normal distributions as priors for $\boldsymbol \theta_{main}$ and $\boldsymbol \theta_{interaction}$, with $\sigma_{interaction} < \sigma_{main}$, *truncated* at $3\sigma_{main}$ and $3\sigma_{interaction}$, respectively. Simulation from the posterior using a geometric adaptive MH step [@zhou2014some], $h_j$ are carried along in the MCMC implementation as latent variables 
3. *A truncated Normal prior and marginalized likelihood (BwTNML).* Marginalize out $\boldsymbol h$ in $f_{\boldsymbol \theta}(\boldsymbol x)$, and use the truncated Normal priors applied to the marginal probabilities for visible variables

@@
